Abstract Binding Trees

### 2015-10-22 paper.tex
Add @freebroccolo as author
Add missing pair

\title{Abstract Binding Trees}
\date{}
\author{Jonathan Sterling}
\maketitle

@@

Via the Grothendieck construction\footnote{Category of elements.}
$\Grothendieck{}{}$ on the operator presheaf $\Operators$ we also have a
category with objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\Member{\vartheta}{f^{*}\Operators} = \vartheta'$.

@@

%%% \subsection{Renaming of Symbols}
%%%
%%% The renaming of symbols in abstract binding trees is defined inductively by the
%%% judgment $\IsRenaming{\psi}{M}{M'}$, where
%%% $\Member{\psi}{\Hom{\SCtx}{\FS{M}}{-}}$
%%%
%%% \begin{gather*}
%%% \end{gather*}

>>>>

\title{Abstract Binding Trees}
\date{}
\author{Jon Sterling and Darin Morrison}
\maketitle

@@

Via the Grothendieck construction\footnote{Category of elements.}
$\Grothendieck{}{}$ on the operator presheaf $\Operators$ we also have a
category with objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\Member{\vartheta}{f^{*}\Operators}\Pair{\Upsilon'}{\varrho'} = \vartheta'$.

@@
